Insights Into Computational Reproducibility in Plant Pathology and a Way Forward

### 2020-12-07 analysis/paper/paper.Rmd
Use TPP citation style

---
title: "Insights Into Computational Reproducibility in Plant Pathology and a Way Forward"
author:
  - Adam H. Sparks:
      email: Adam.Sparks@usq.edu.au
      institute: USQ
      correspondence: true
  - Emerson Del Ponte:
      institute: UFV
  - Kaique dos Santos Alves:
      institute: UFV
  - Zachary Foster: 
      institute: OSU
  - Niklaus J Grünwald: 
      institute: ARS
institute:
  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Queensland, Australia
  - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
  - OSU: Department of Botany and Plant Pathology, Oregon State University, Corvallis, OR, USA
  - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis, OR, USA
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  officedown::rdocx_document:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
        - '--lua-filter=scholarly-metadata.lua'
        - '--lua-filter=author-info-blocks.lua'
        - '--lua-filter=pagebreak.lua'
      tables:
        layout: autofit
        width: 1.0
        caption:
          style: Table Caption
          pre: 'Table '
          sep: ': '
        conditional:
          first_row: true
          first_column: false
          last_row: false
          last_column: false
          no_hband: false
          no_vband: true
bibliography: references.bib
csl: "../templates/phytopathology.csl" # Insert path for the bib-style
abstract: |
  Open research practices have been highlighted extensively during the last ten years in many fields of study as essential standards needed to promote transparency and reproducibility of scientific results. In fact, scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared; and analyses conducted. Openly sharing protocols, data and computational code are central for current scholarly dissemination and communication, but in many fields, including plant pathology, adoption of these practices has been slow. We randomly selected 300 articles published from 2012 to 2018 across 21 journals representative of the pathology discipline, and assigned them scores reflecting their openness and reproducibility. We found that most of the articles were not very open, failing to share data or code in a meaningful way. We propose that using open source tools for producing open and reproducible work and analysis is advantageous, benefiting not just readers, but the authors as well and provide ideas and tools to promote open, reproducible research practices among plant pathologists.
keywords: |
  open science; open data; reproducible research; FAIR data
highlights: |
  Open research practices are highlighted extensively in the broader scientific community. Our survey of 300 randomly selected articles from 2012 to 2018 indicates that we have work to do in this area as plant pathologists with most articles scoring low in openness and reproducibility.
---

>>>>

---
title: "Insights Into Computational Reproducibility in Plant Pathology and a Way Forward"
author:
  - Adam H. Sparks:
      email: Adam.Sparks@usq.edu.au
      institute: USQ
      correspondence: true
  - Emerson Del Ponte:
      institute: UFV
  - Kaique dos Santos Alves:
      institute: UFV
  - Zachary Foster: 
      institute: OSU
  - Niklaus J Grünwald: 
      institute: ARS
institute:
  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba, Queensland, Australia
  - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
  - OSU: Department of Botany and Plant Pathology, Oregon State University, Corvallis, OR, USA
  - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis, OR, USA
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  officedown::rdocx_document:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
        - '--lua-filter=scholarly-metadata.lua'
        - '--lua-filter=author-info-blocks.lua'
        - '--lua-filter=pagebreak.lua'
      tables:
        layout: autofit
        width: 1.0
        caption:
          style: Table Caption
          pre: 'Table '
          sep: ': '
        conditional:
          first_row: true
          first_column: false
          last_row: false
          last_column: false
          no_hband: false
          no_vband: true
bibliography: references.bib
csl: "../templates/TPP.csl" # Insert path for the bib-style
abstract: |
  Open research practices have been highlighted extensively during the last ten years in many fields of study as essential standards needed to promote transparency and reproducibility of scientific results. In fact, scientific claims can only be evaluated based on how protocols, materials, equipment and methods were described; data were collected and prepared; and analyses conducted. Openly sharing protocols, data and computational code are central for current scholarly dissemination and communication, but in many fields, including plant pathology, adoption of these practices has been slow. We randomly selected 300 articles published from 2012 to 2018 across 21 journals representative of the pathology discipline, and assigned them scores reflecting their openness and reproducibility. We found that most of the articles were not very open, failing to share data or code in a meaningful way. We propose that using open source tools for producing open and reproducible work and analysis is advantageous, benefiting not just readers, but the authors as well and provide ideas and tools to promote open, reproducible research practices among plant pathologists.
keywords: |
  open science; open data; reproducible research; FAIR data
highlights: |
  Open research practices are highlighted extensively in the broader scientific community. Our survey of 300 randomly selected articles from 2012 to 2018 indicates that we have work to do in this area as plant pathologists with most articles scoring low in openness and reproducibility.
---
